Geometric variational problems

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
RJR--got to run; tornado warning

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to 
New York for one or two weeks in the summers. Fordham University 
recently constructed a seminar/collaboration space specifically
for collaborative research, and URs will base there activitied from here.

>>>>

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to 
New York for one or two weeks in the summers. Fordham University 
recently constructed a seminar/collaboration space specifically
for collaborative research, and the URs will office space with desks
there.
